IARC Research Paper

### 2017-05-28 IARC_Paper/Paper.tex
Time to get working on this

\usepackage{geometry}
\geometry{letterpaper}
\usepackage{doc}
\usepackage{url}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{fancyhdr}

\title{IARC Research Paper}
\author{Texas Aerial Robotics}
\date{February 25, 2017}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\cfoot{\thepage\ of \pageref{LastPage}}

@@

\abstract{
Texas Aerial Robotics will compete in Mission 7 of the International Aerial Robotics Competition (IARC) in 2017. The goal is to direct Roombas (iRobot Create 2's), known as ground robots, using a quadcopter. We use an Intel stereo camera (put name here) for vision, a Nvidia Jetson for vision processing, and a Pixhawk for controlling the quadcopter. 
}

@@

\section{Safety}

>>>>

\usepackage[margin=1in]{geometry}
\geometry{letterpaper}
\usepackage{doc}
\usepackage{url}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{fancyhdr}

\title{IARC Research Paper}
\author{Texas Aerial Robotics \\ \\ Samid Ahmed, Adam Bays, Nicholas Boeker, Jeremie Gallegos, \\ Eric Johnson, Aaron Karns, Cameron Lane, Juliette Licon, \\ Mark Loveland, Jonathan Lu, Umer Salman, Ethan Starr, Jacob Yanez} % A note about authors:  list only those who actually contributed to the writing of this paper.  All the members of the team should not be listed as authors unless they all wrote at least a page of the material for the paper.

\date{May 28, 2017}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\cfoot{\textsf{Page \thepage\ of \pageref{LastPage}}}

@@

\abstract{
Texas Aerial Robotics will compete in Mission 7 of the International Aerial Robotics Competition (IARC) in 2017. The goal is to direct Roombas (iRobot Create 2's), known as ground robots, using a quadcopter. We use a camera (put name here) for vision, a Nvidia Jetson for vision processing, and a Pixhawk for controlling the quadcopter. 
}

@@

\section{Safety}
\subsection{Pre-flight Checklist}
\begin{enumerate}
	\item Make sure lidar and pix flow are not covered
	\item Make sure that escs are plugged in to the right ports. 
	\item Make sure that the props are on in the correct direction. 
	\item Make sure that the props are not upside down
	\item Make sure drone is level before powering on
	\item Hold safety button
	\item Make sure ground station has good telemetry
	\item Verify critical sensors are giving good data
	\item Make sure everyone is clear of drone 
\end{enumerate}
